---
title: "Final Term Project 2022"
output: 
  github_document :
    toc: true
   
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
library(far)
library(MASS)
library(pracma)
library(kableExtra)
library(wooldridge)
library(dplyr)
library(ggplot2)
library(matlib)
library(lubridate)
library(ggplot2)
library(rcompanion)
library(trelliscopejs)

```

[1. Abstract](# Abstract)  

[2. Introduction](# Introduction)  

[3. Data](# Data)  

[4. Methodology](# Methodology)  




# Abstract

Transfer is important in the public transit since 


# Introduction


# Data Description


## Description of Test Network(120 Line)  


## Description of Smart Card Data

```{r}

```



## Data Pre-prrocessing




## Assumption



## Basic Statistics


# Methodology





#


## wow

sadsadsadsadsadsadsadsad


## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
